systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2005-09-07 paper/trunk/systemfit_intro.tex
systemfit_intro.tex: modified/extended introduction
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@572 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Another reason to estimate an equation system simultaneously are
cross-equation parameter restrictions. These restrictions can be
tested and/or imposed only in a simultaneous estimation
approach. Especially the economic theory suggests many cross-equation
restriction.

The \pkg{systemfit} package provides the capability to estimate
linear and non-linear equation systems in \proglang{R}. Compared to
other statistics and econometrics software the (advanced) user can
control many important details of the estimation procedure. On the
other hand these user options have reasonable defaults that also
beginners can easily use the provided functions.

>>>>

Another reason to estimate an equation system simultaneously are
cross-equation parameter restrictions. These restrictions can be
tested and/or imposed only in a simultaneous estimation
approach. Especially the economic theory suggests many cross-equation
restrictions.

The \pkg{systemfit} package provides the capability to estimate
linear and non-linear equation systems in \proglang{R}.
Although linear and non-linear equation systems can be estimated
with several other statistical and econometric software packages
(e.g. \proglang{SAS}, \proglang{EViews}, \proglang{TSP}),
using \pkg{systemfit} has several advantages.
First, all estimation procedures are publicly available in the source code.
Second, the estimation algorithms can be easily modified to meet specific
requirements.
Third, the (advanced) user can control many important details of the
estimation procedure that are generally not available in other software
packages.
On the other hand these user options have reasonable defaults that also
beginners can easily use the provided functions.
